---
title: "explanatory data project1"
author: "Jiaoping"
date: "May 13, 2015"
output: html_document
---

load pakacge
```{r}
library(sqldf)
```

load agian
```{r}
library(sqldf)
```

load sepecific data into R

```{r}
file<-'household_power_consumption.txt'
con<-file(description=file,open="r")
mySql <- "SELECT * from file WHERE Date = '1/2/2007' OR Date = '2/2/2007'"
myFile <- "household_power_consumption.txt"
myData <- read.csv2.sql(myFile,mySql)
close(con)
```

look at the data
```{r,cache=F}
head(myData,n=3)
```

as.date
```{r}
x<-as.Date(myData$Date, format="%d/%m/%Y")
```

```{r}
datetime <- paste(myData$Date, myData$Time)
xx<-strptime(datetime, format="%d/%m/%Y %H:%M:%S")
```


make plot1 histogrm and stored in the rmd folder
```{r}
png(filename='plot1.png',width=480,height=480,units='px')
with(myData,hist(Global_active_power, xlab="Global Active Power(kilowatts)", main="Global Active Power",col="red"))
dev.off()
```

make plot2
```{r}
png(filename='plot2.png',width=480,height=480,units='px')
with(myData,plot(xx,Global_active_power, ylab="Global Active Power(kilowatts)", main="Global Active Power",type="l"))
dev.off()
```

```{r}
str(myData)
```

make plot 3


```{r}
png(filename="plot3.png",width=480,height=480,units="px")
ncol<-c("black","red","blue")
lbls<-c("Sub_metering_1","Sub_metering_2","Sub_metering_3")
plot(x=xx,y=myData$Sub_metering_1,ylab="Energy sub meering", xlab="",type="l",col="black")
lines(x=xx,y=myData$Sub_metering_2,ylab="Energy sub meering", xlab="",type="l",col="red")
lines(x=xx,y=myData$Sub_metering_3,ylab="Energy sub meering", xlab="",type="l",col="blue")
legend("topright",c("Sub_metering_1","Sub_metering_2","Sub_metering_3"),col=ncol,lty="solid")
     y<-dev.off()
```

make plot 4

```
```{r}
png(filename="plot4.png",width=480,height=480,units="px")
par(mfrow=c(2,2))
with(myData,hist(Global_active_power, xlab="Global Active Power(kilowatts)", main="Global Active Power",col="red"))
with(myData,plot(xx,Voltage,xlab='datetime',ylab='Voltage',type='l'))
ncol<-c("black","red","blue")
lbls<-c("Sub_metering_1","Sub_metering_2","Sub_metering_3")
plot(x=xx,y=myData$Sub_metering_1,ylab="Energy sub meering", xlab="",type="l",col="black")
lines(x=xx,y=myData$Sub_metering_2,ylab="Energy sub meering", xlab="",type="l",col="red")
lines(x=xx,y=myData$Sub_metering_3,ylab="Energy sub meering", xlab="",type="l",col="blue")
legend("topright",c("Sub_metering_1","Sub_metering_2","Sub_metering_3"),col=ncol,lty="solid")
with(myData,plot(xx,Global_reactive_power, type="l",))
dev.off()
```











